3 slides to convince you that it's endogenous TFP

### 2018-01-31 Latex/Basu_propositions/propositions.tex
updated Basu presentation
another little change to Basu presentation

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
\end{align*}

@@

$\Psi$ is a final-good-specific exogenous technology process.

>>>>

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{s.t.} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 & \text{but not internalizing} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
\end{align*}

@@

$\Psi$ is a final-good-specific exogenous deterministic technology process.
